Assessing the Replicability of Psychological Science Through Pedagogy

### 2016-08-24 paper/paper.Rmd
Color of rep graphs

```{r, fig.height=9, fig.width=6}
library(png)
layout(matrix(1:24,nr=6,byr=T))
for (key in project_plan$project_key) {
  orig <- readPNG(paste0("../figures/",key,"-original.png"))
  rep <- readPNG(paste0("../figures/",key,"-replication.png"))

@@

}
```

>>>>

```{r, fig.height=9, fig.width=6}
  # colors:268bd2 859900 dc322f
library(png)
layout(matrix(1:24,nr=6,byr=T))
project_key_sorted <- c(
  "jsalloum","ehermann","salehi", # rep = 1
  "mkeil","smraposo","jedtan","rhiac","lampinen", # rep=.5
  "jreynolds","jmarias","auc" #rep = 0
)
for (key in project_key_sorted) {
  orig <- readPNG(paste0("../figures/",key,"-original.png"))
  rep <- readPNG(paste0("../figures/",key,"-replication.png"))

@@

}
# Add legend
legend <- readPNG(paste0("../figures/Replication-Legend.png"))

plot(c(0, 100), c(0, 100), type = "n", xlab="", ylab="", axes=F)
  rasterImage(legend, 0, 0, 100, 100, interpolate=FALSE)
```
